---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

                                Homework:

Classification And REgression Training

The train() function
The core of caret’s functionality is the train() function.

train() is the function that we use to “train” the model. That is, train is the function that will “learn” the relationship between mpg and wt.

When training a model using train(), you only need to tell it a few things:
– The dataset you’re working with
– The target variable you’re trying to predict (e.g., the mpg variable)
– The input variable (e.g., the wt variable)
– The machine learning method you want to use (in this case “linear regression”)


```{r}
library(ISLR)
library(caret)
library(ggplot2)
model.mtcars_lm <- train(mpg ~ wt     #wt	Weight (1000 lbs)
                        ,data = mtcars
                        ,method = "lm"
                        )
summary(model.mtcars_lm)
model.mtcars_lm
#~~~~~~~~~~~~~~~~~~~~~~~~~~
# Retrieve coefficients for
#  - slope
#  - intercept
#~~~~~~~~~~~~~~~~~~~~~~~~~~

coef.icept <- coef(model.mtcars_lm$finalModel)[1]
coef.slope <- coef(model.mtcars_lm$finalModel)[2]


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Plot scatterplot and regression line
#  using ggplot()
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

ggplot(data = mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_abline(slope = coef.slope, intercept = coef.icept, color = "red")
```


                                     Classwork:


## Loading data

```{r}
library(ggplot2)
mpg
df <- mpg
data(df)
dim(df)
str(df)
```

## Exploring data

```{r}
#plot(df)
table(df$hwy)

library(ggplot2)
library(tidyverse)
#ggplot(df) +
#  geom_bar(aes(x = Species, fill = Species))
hist(df$hwy)

sapply(df, function(x) sum(is.na(x))) 
  
```


## Some info

Now we are splitting the data $A=b_{4} $

$$ \epsilon = \frac{5}{7}$$


## Split data

```{r}
library(caret)
set.seed(825)

trainIndex <- createDataPartition(df$hwy, p = .8, 
                                  list = FALSE, 
                                  times = 1)
head(trainIndex)

training <- df[ trainIndex,]
test  <- df[-trainIndex,]

nrow(training)
```


##  Pre-Processing

```{r}
preProcValues <- preProcess(training, method = c("center", "scale"))

trainTransformed <- predict(preProcValues, training)
testTransformed <- predict(preProcValues, test)


```

## Training

### KNN

```{r}
fitControl <- trainControl(## 10-fold CV
                           method = "cv",
                           number = 10
                           ## repeated ten times
                           #repeats = 10
                           )

KnnGrid <-  expand.grid(k = 1:100)


FitKnn <- train(hwy ~ displ + class, data = trainTransformed, 
                 method = "knn", 
                 trControl = fitControl,
                 verbose = FALSE, 
                 tuneGrid = KnnGrid)
FitKnn
summary(FitKnn)
plot(FitKnn)


FitKnn$bestTune
caret::RMSE(pred = predict(FitKnn, testTransformed), 
            obs = testTransformed$hwy)
caret::R2(pred = predict(FitKnn, testTransformed), 
            obs = testTransformed$hwy)

KnnGrid3 <-  expand.grid(k = 3)
FitKnn3 <- train(hwy ~ ., data = trainTransformed, 
                 method = "knn", 
                 trControl = fitControl,
                 verbose = FALSE, 
                 tuneGrid = KnnGrid3)
caret::R2(pred = predict(FitKnn3, testTransformed), 
            obs = testTransformed$hwy)
```


```{r}

#KnnGrid <-  expand.grid(k = 1:100)
 


FitLm <- train(hwy ~ displ + class, data = trainTransformed, 
                 method = "glm", 
                 trControl = fitControl
                 #tuneGrid = KnnGrid
                )
FitLm
summary(FitLm)
str(FitLm)
summary(FitLm$finalModel)

FitLm$results$Rsquared
FitLm$results$RsquaredSD

FitLm$bestTune

caret::R2(pred = predict(FitLm, testTransformed), 
            obs = testTransformed$hwy)

#plot(FitLm)
```


### Neural Network

```{r}
Fitnn <- train(hwy ~ ., data = trainTransformed, 
                 method = "nnet", 
                 trControl = fitControl
                 #tuneGrid = KnnGrid
                )
Fitnn

caret::R2(pred = predict(Fitnn, testTransformed), 
            obs = testTransformed$hwy)

```

